Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-03-25 papers/intro_paper/results_lvc.tex
updated Table-II to include IMR values of Mf,af from our GR runs, and not the LVC publications

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for LVC values
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\input{table_lvc_results}
\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,2)$ QNM, and the mass and spin of the remnant object estimated from 
the QNM frequencies using the $\pSEOB$ model. We indicate with a star the GW events that were analysed in this paper, the other events were examined in Ref.~\cite{Abbott:2020jks}. \abhi{[AG: There aren't Mf-chif-IMR results for 0630 in the GWTC-2 TGR paper, probably because PyRING did not run on it. The current values are from the GWTC-2 catalog paper. The numbre is red is source-frame; needs to be converted to detector-frame.]}}
\label{tab:qnm_o1o2_results}
\end{table*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for LVC values
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\input{table_lvc_results}
\caption{The median and symmetric 90\% credible intervals of the remnant properties. The first two columns represent the frequency and damping time of the $(2,2)$ QNM measured using the $\pSEOB$ model. The next two columns are the mass and spin of the remnant object estimated from the complex QNM frequencies by inverting the fitting formula in~\cite{Berti:2005ys}. The last two columns represent final mass and spin estimates predicted using NR fitting formulae from a $\SEOB$ (GR) parameter estimation.}
\label{tab:qnm_o1o2_results}
\end{table*}
